Plots

### 2023-09-06 Code/Plots.Rmd
Remove unneccessary code

```{r}
opar <- par()
par(mfrow = c(1,2))
pdf(file = "BoxplotFinals.pdf")
boxplot(RxnTime ~ Year, data = men_finals, xlab = "Year", ylab = "Reaction Time in seconds")
boxplot(RxnTime ~ Year, data = men_finals, xlab = "Year", ylab = "Reaction Time in seconds")
dev.off()
par(opar)
```

```{r}
#ggplot(data = win, aes(x = strength_diff)) + geom_boxplot() + theme_minimal()
ggplot(data = men_finals, aes(x=Year, y = RxnTime)) + geom_boxplot() + theme_minimal()
```

```{r}
library(gridExtra)
library(ggplot2)
final <- ggplot(men_finals, aes(x = Year, y = RxnTime, group = Year)) +
  geom_boxplot(fill = "lightblue", color = "darkblue") +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.1, 0.225),
                            breaks = seq(0.1, 0.225, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(1998,2023),
                                              breaks = seq(1997, 2022, 2))

pooled <- ggplot(men_pooled, aes(x = Year, y = RxnTime, group = Year)) +
  geom_boxplot(fill = "orange1", color = "orangered4") +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.1, 0.225),
                            breaks = seq(0.1, 0.225, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(1998,2023),
                                              breaks = seq(1997, 2022, 2))
#both <- grid.arrange(final,pooled, ncol=1)
grid.arrange(final,pooled, ncol=1)
#ggsave(filename="Finals_Pooled_Boxplot.pdf", path = "../Manuscript", plot=both, height = 6, width = 6)
```

>>>>

```{r}
library(ggplot2)
ggplot(men_pooled, aes(x = Year, y = RxnTime, group = Year)) +
  geom_boxplot(fill = "orange1", color = "orangered4") +
  labs(x = "Year", y = "Reaction Time (s)") +
       scale_y_continuous(limits = c(0.1, 0.225),
                            breaks = seq(0.1, 0.225, 0.025)) +
  expand_limits(y = 0.1) + scale_x_continuous(limits = c(1998,2024),
                                              breaks = seq(1999, 2024, 2))
ggsave(filename="Boxplot.pdf", path = "../Manuscript", height = 4, width = 6)
```

```{r}
library(tidyr)
library(ggplot2)
nineteen <- read.csv("../Data/2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(nineteen) <- c("Athlete", "Country", "2019 Heats", "2019 Semifinals", "2019 Finals", "2022 Heats", "2022 Semifinals", "2022 Finals")
nineteen <- nineteen[, -c(1,2)]
df_long <- tidyr::pivot_longer(nineteen, cols = everything(), names_to = "Column", values_to = "Time")
df_long$Column <- factor(df_long$Column, levels = c("2019 Heats", "2019 Semifinals", "2019 Finals", "2022 Heats", "2022 Semifinals", "2022 Finals"))
rank1 <- ggplot(df_long, aes(x = Column, y = Time)) +
  geom_point() +
  labs(y = "Reaction Time", x = "", title = "2019 vs 2022") +
  ylim(0.08, 0.22) +
  theme_minimal()
```

```{r}
library(tidyr)
library(ggplot2)
twentythree <- read.csv("../Data/2022vs2023.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(twentythree) <- c("Athlete", "Country", "2022 Heats", "2022 Semifinals", "2022 Finals", "2023 Heats", "2023 Semifinals", "2023 Finals")
twentythree <- twentythree[, -c(1,2)]
df_long <- tidyr::pivot_longer(twentythree, cols = everything(), names_to = "Column", values_to = "Time")
df_long$Column <- factor(df_long$Column, levels = c("2022 Heats", "2022 Semifinals", "2022 Finals", "2023 Heats", "2023 Semifinals", "2023 Finals"))
rank2 <- ggplot(df_long, aes(x = Column, y = Time)) +
  geom_point() +
  labs(y = "Reaction Time", x = "", title = "2022 vs 2023") +
  ylim(0.08, 0.22) +
  theme_minimal()
```

```{r}
library(tidyr)
library(ggplot2)
national <- read.csv("../Data/NatVSWorld.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(national) <- c("Athlete", "Country", "National Heats", "National Semifinals", "National Finals", "2023 Heats", "2023 Semifinals", "2023 Finals", "Data Source")
national <- national[, -c(1,2, 9)]
df_long <- tidyr::pivot_longer(national, cols = everything(), names_to = "Column", values_to = "Time")
df_long$Column <- factor(df_long$Column, levels = c("National Heats", "National Semifinals", "National Finals", "2022 Heats", "2022 Semifinals", "2022 Finals"))
rank3 <- ggplot(df_long, aes(x = Column, y = Time)) +
  geom_point() +
  labs(y = "Reaction Time", x = "", title = "2022 National vs International") +
  ylim(0.08, 0.22) +
  theme_minimal()
```

```{r}
library(gridExtra)
rank_scatter <- grid.arrange(rank1, rank2, rank3, ncol = 1)
ggsave(filename = "RankScatterPlots.pdf", path = "../Manuscript", plot=rank_scatter, height = 9, width = 7)
```
